---
title: "R Notebook"
output: html_notebook
---
```{r}
deps = c("tidyverse", "rvest", "stringr", "here", "magrittr", "dplyr")
install.packages(deps)
library(tidyverse)
library(magrittr)
library(ggplot2)
library(dplyr)
```

```{r}
setwd('/home/rerissondcsm/reclamacoes-do-gf')
reclamacoes <- read.csv("data/1-reclamacoes-selecionadas/reclamacoes-avaliadas.csv")
reclamacoes <- reclamacoes %>% mutate(length = str_length(reclamacao))
```

```{r}

media_orgaos <- aggregate(reclamacoes$length, list(orgao = reclamacoes$orgao), mean)
media_orgaos %>% View

```

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
