---
title: "R Notebook"
output: html_notebook
---
```{r}
deps = c("tidyverse", "rvest", "stringr", "here", "magrittr", "dplyr", "readr")
install.packages(deps)
library(tidyverse)
library(magrittr)
library(ggplot2)
library(dplyr)
library(readr)
```

##Questão 1
```{r}
media_orgaos <- aggregate(reclamacoes$length, list(orgao = reclamacoes$orgao), mean)

barplot(media_orgaos$x, main='Média dos tamanhos das reclamações por orgão', names.arg = c("Anac", "INSS"))
```
Podemos perceber que o tamanho das reclamações direcionadas à ANAC são em média muito maiores. Posteriormente pretendemos relacionar neste estudo o tamanho das reclamações com a insatisfação associada a elas no experimento humano e na análise de sentimentos.

##Questão 2
```{r}

```



```{r}
setwd('/home/filipegl/Documentos/metodologia/reclamacoes-do-gf')
reclamacoes <- read.csv("data/1-reclamacoes-selecionadas/reclamacoes-avaliadas.csv")
reclamacoes <- reclamacoes %>% mutate(length = str_length(reclamacao))
avaliacoes <- read_csv("data/3-avaliacao-humana/avaliacoes-20180610.csv")
avaliacoes <- avaliacoes %>% 
              select(avaliador = `Matricula`, 
                      id = `ID da reclamação`, 
                      insatisfacao = `Grau de insatisfação`)
```


```{r}
x <- rep(1:5, each=7)
y <- rnorm(10*7)
boxplot(length~mediana,data=reclamacoes,col=rainbow(length(unique(x))), main="Média das reclamações por nível de insatisfação",
   xlab="Nível de insatisfação", ylab="Tamanho das reclamações") 

agrupar <- reclamacoes %>% group_by(reclamacoes$mediana) %>% summarise(media = mean(length)) 

barplot(agrupar$media, names = agrupar$mediana,
  xlab = "Nível de insatisfação", ylab = "Tamanho das reclamações",
  main = "Média das reclamações por nível de insatisfação")
```


##  Questao 3
```{r}
avaliacoes %>% 
  filter((insatisfacao > 5 | insatisfacao < 1))
```


## Questao 4
```{r}
avaliacoes %>% 
  group_by(id) %>% 
  count() %>%
  ungroup() %>% 
  summarise(media = mean(n))
```


Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
